Estimating individual subjective values of emotion regulation strategies

### 2022-08-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
corrected mistake in figure caption
knitted document
Update Manuscript_ERED_Stage2.Rmd

---
title             : "Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Subjective values of emotion regulation strategies"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Denise Dörfel"
    orcid         :
    affiliation   : "1"
    role          :
      - Conceptuatlization
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Writing - review & editing 
affiliation       :
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote        :
abstract          : |
 Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
 In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
 Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
 Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
 Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
 However, SVs of ER strategies have not been determined so far. 
 We present a paradigm that is suitable for determining individual SVs of ER strategies. 
 Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
 Relations of SVs to personality traits will be explored.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
wordcount         : "XXXXX"
bibliography      : ["ER_ED.bib"]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# load workspace variables from analyses_ERED.R script
load(here("06_Paper","ER-ED","Workspace_ERED.RData"))

@@

```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

@@

```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

>>>>

---
title             : "Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Subjective values of emotion regulation strategies"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Denise Dörfel"
    orcid         :
    affiliation   : "1"
    role          :
      - Conceptuatlization
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Methodology
      - Writing - review & editing 
affiliation       :
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote        :
abstract          : |
 Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
 In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
 Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
 Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
 Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
 However, SVs of ER strategies have not been determined so far. 
 We present a paradigm that is suitable for determining individual SVs of ER strategies. 
 Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
 Relations of SVs to personality traits will be explored.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
wordcount         : "XXXXX"
bibliography      : ["ER_ED.bib"]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# load workspace variables from analyses_ERED.R script
load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))

@@

```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the arousal rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

@@

```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the arousal rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}
